Balsa: A Compact Line Notation Based on SMILES

### 2022-07-03 manuscript.tex
Adds figure for conformational transformations. Closes #17

It is sometimes useful to manipulate a configuration in a way that preserves the relative three-dimensional positioning of neighbor atoms. This process is called \textit{transformation}. Five operations suffice to transform any configuration into any other:

\begin{itemize}
    \item{Virtualize. Replaces an atomic hydrogen neighbor with a virtual hydrogen. If the deleted bond was first in the bond ordering, toggle the configurational descriptor.}
    \item{Reify. Replaces a virtual hydrogen with an atomic hydrogen neighbor. The bond ordering must place the new neighbor in the second position.}
    \item{Swap. Exchanges any two bonds ordered second or higher while simultaneously toggling the configurational descriptor.}
    \item{Slide Left. Re-orders a bond from the first position to the second position. Disabled if the central atom carries a virtual hydrogen.}
    \item{Slide Right. Re-orders a bond from the second position to the first position. Disabled if the central atom carries a virtual hydrogen.}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Configurational Transformations.}
    \label{fig:iconfigurational-transformations}
\end{figure}

>>>>

It is sometimes useful to manipulate a configuration in a way that preserves the relative three-dimensional positioning of neighbor atoms. This process is called \textit{transformation}. Four operations suffice to transform any configuration into any other (Figure~\ref{fig:configurational-transformations}):

\begin{itemize}
    \item{Virtualize. Replaces an atomic first hydrogen child with a virtual hydrogen.}
    \item{Reify. Replaces a virtual hydrogen with an atomic hydrogen first child.}
    \item{Swap Children. Exchanges any two children while simultaneously toggling the configurational descriptor.}
    \item{Swap Parent. Exchanges parent for first child. Disabled if the central atom carries a virtual hydrogen.}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{configurational-transformations.pdf}
    \caption{Configurational Transformations.}
    \label{fig:configurational-transformations}
\end{figure}
